\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-15 latex/article_vol2.tex
Added figure to describe the structure of clean() + example mosaic plot pdf.

@@

\hl{metatext here: blabla more can be done blabla...}

Though the \R{clean()} function is very easy to use, it should not be mistaken to be inflexible. A large number of function arguments allows for the cleaning overview document to be molded as the user sees best. Below, we present a selection of these arguments. We do this under two distinct headlines to emphasize that two levels of control are available when using \R{clean()}. Either, we can control the \hl{[something]. Essentially, this is everything but SVC-functions.} \\

\hl{Note that the terminology "SVC"-step (referring to the summarize/visualize/check-step) needs to be introduced in this part, as it is used in Table \ref{table.cleanFormals}.}

>>>>

\begin{figure}
\begin{description}
\item[Input] A dataset
	\begin{itemize} 
		\item This should be of type \R{data.frame} or \R{tibble}
	\end{itemize}
\item[Create contents] For each variable in the dataset, do the following:
	\begin{description}
		\item[Stage 1:] Pre-checks 
			\begin{itemize}
				\item Is the variable suitable for summarization, visualization and checks?
				\begin{description}
					\item[Yes:] Go to stage 2 
					\item[No:] Move on to the next variable
				\end{description}
			\end{itemize}
		\item[Stage 2:] SVC-steps
			\begin{description}
				\item[Summarize] Call \R{summarize()} to produce a summary table describing the variable. What features enter this table depends on the data class of the variable.
				\item[Visualize]  Call \R{visualize()} to produce a plot visualizing the distribution of the variable. 
				\item[Check]  Call \R{check()} to apply quality- and error checks to the variable. What checks are used depends on the data class of the variable.
			\end{description}
	\end{description}
\item[Output] Files for a overview document 
	\begin{itemize}
		\item Always a \R{rmarkdown} (.Rmd) file
		\item Possible also a html or pdf file
	\end{itemize}
\end{description}
\caption{\hl{quite odd having a figure like this? maybe do a flowchart?}}
\label{figure:cleanStructure}
\end{figure}

@@

\hl{metatext here: blabla more can be done blabla...} \\

Though the \R{clean()} function is very easy to use, it should not be mistaken to be inflexible. A large number of function arguments allows for the cleaning overview document to be molded as the user sees best. Below, we present a selection of these arguments in sections \hl{xx} and \hl{xxx}. We do this under two distinct headlines to emphasize that two levels of control are available when using \R{clean()}. Either, we can control the \hl{[something] - essentially, this is everything but SVC-functions - } or we can control what quality assessments and descriptions each variable are subjected to. In order to understand this distinction, a brief glimpse of the inner structure of \R{clean()} might be useful. This can be obtained from Figure~\ref{figure:cleanStructure}. \hl{segway to next bit or just something to end the paragraph}
